\documentclass[MiniProjectMain]{subfiles}
\begin{document}

\chapter{Requirements}
This chapter specifies the requirements stated for this project, stated in the assignment.
Further it states the chosen requirements, delimiting the implementation of the project.

\section{Assignment requirements}
\subsection{Cyclic encoder}
A cyclic encoder function shall be implemented in MATLAB

\begin{itemize}

\item 
The function must accept two inputs:

	\begin{itemize}
	\item A Generator polynomial
	\item A message vector
	\end{itemize}

\item The Function must have one output:

	\begin{itemize}
	\item A code vector
	\end{itemize}
	
\end{itemize}

\subsection{Meggitt decoder}
A cyclic decoder based on the Meggitt Algorithm shall be implemented in MATLAB.

\begin{itemize}

\item 
The function must accept four inputs:

	\begin{itemize}
	\item Received vector
	\item Generator polynomial
	\item Code length: \textit{n}
	\item Message length: \textit{k}
	\end{itemize}

\newpage
\item The Function must have three outputs:

	\begin{itemize}
	\item Error vector
	\item Code vector
	\item A tag, indicating if recieved vector is:
		\subitem decodable, or
		\subitem undecodable but detectable
	\end{itemize}
	
\end{itemize}

\subsection{Conditions for operation}
Conditions for operation, stated in the assignment, are as follows:

\begin{itemize}

\item Code length: \textit{15}
\item Message length: \textit{7}
\item Given generator polynomial:
\begin{align}
g(X) &= 1 + X^4 + X^6 + X^7 + X^8
\end{align}

\end{itemize}

\newpage
\section{Implementation requirements}
These are requirements that the implementing group has chosen for the project.
\begin{itemize}
\item 
The MATLAB code for this project shall be implemented with a GUI that visualizes the flow and operation of the Meggitt decoder.

\item
The implementation shall be generalized so that \textit{n}, \textit{k} and the generator polynomial can be user specified.

\item
The implementation shall only accept double error correcting polynomials.

\item
The user shall be able to specify any error pattern of length: \textit{n}.

\item
The implementation shall only process (encode, affect with error and decode) one message vector at a time.

\item
It shall be possible step through every cycle of the decoding or run it all at once. 

\end{itemize}

\end{document}
